### 2018-01-26 includes/problems.tex
updated description of transformers

    The \texttt{transformed} suite contains problems generated by using one root problem and transforming it with \transformer{} into many similar problems. They are described below:

    \todo{Federico: fill in descriptions.}

    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name} & \textbf{Description} \\ \hline
        Amazon        & \\ \hline
        Regex         & \\ \hline
    \end{tabular}

@@

>>>>

    \todo{Federico: fill in descriptions. First draft - Federico}

    The \texttt{transformed} suite contains benchmarks derived from existing seed problems by iteratively applying \transformer{}.
    Every problem in the suite is named according to its seed and the transformations it undertook. For example, a hypothetical file named ``seed-fuzz-graft.smt2'' began as a file named ``seed.smt'' and was transformed twice, first by fuzz and then by graft. See Table~\ref{tbl:transformed} for an overview description of the suite.

    The suite is divided into two categories. The first category, labeled Amazon, started as two seed files.
    The first seed, z3-regex-1.smt2, encodes the assertions ``S not in aaabbb*'' and ``S in aaa*bbb*'' for a string constant S,
    while the second seed, z3-regex-2-negative.smt2, encodes the assertions ``S in aaabbb*'' and ``S not in aaa*bbb*''. 
    \todo{Can I say that these problems were deemed industrially relevant by Amazon? Probably not, right?} 
    In total, 516 unique problems were generated from these two seeds.

    The second category, Regex, is seeded by the z3str2 regular expression test suite \cite{} \todo{Is this right? If so where we can cite?}. This test suite contains 42 problems dealing with a wide variety of regular expressions.
    Through accumulative transformations, as before, we were able to produce 10,577 unique benchmarks.

    \begin{table}
    \begin{tabular}{|l|l|r|}
        \hline
        \textbf{Name} & \textbf{Seed}                            & \textbf{Qunatity} \\ \hline
        Amazon        & Two industrial regex membership problems & 516\\ \hline
        Regex         & Z3str2 regular expression test suite     & 10,577\\ \hline
    \end{tabular}
    \caption{\transformer{} generated problem sets.}
    \label{tbl:transformed}
    \end{table}

@@

        \todo{Federico - Can we describe the floating point error we found?}
